### 2018-02-06 project.tex
better define basis

	\begin{definition}
	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ is a basis for $\tau$ if:
	\newline
	1. For all x $\in$ U $\in \tau$, there exists B $\in$ $\mathcal{B}$ where x $\in$ B $\subseteq$ U $\in \tau$
	\newline
	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
	\end{definition}

>>>>

	\begin{definition}
		A collection of sets \(\mathcal{B}\subseteq\mathcal{P}(X)\) is
		called a basis if:
		\begin{enumerate}
			\item For all \(x\in X\), there exists \(B\in\mathcal{B}\) such that
			\(x\in B\).
			\item  For all \(B_1,B_2 \in \mathcal{B}\) with \(x \in B_1 \cap B_2\), there exists \(B_3 \in \mathcal{B}\) with
			\(x\in B_3 \subseteq B_1 \cap B_2\).
		\end{enumerate}
	  The set \(\{\bigcup\mathcal{B}':\mathcal{B}'\subseteq\mathcal{B}\}\)
		is called the topology generated by \(\mathcal{B}\).
	\end{definition}

	\begin{theorem}
		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
	\end{theorem}

	\begin{theorem}
	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ generates $\tau$ if:
	\newline
	1. For all x $\in$ U $\in \tau$, there exists B $\in$ $\mathcal{B}$ where x $\in$ B $\subseteq$ U $\in \tau$
	\newline
	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
\end{theorem}
